### 2025-06-23 evaluating-prediction-accuracy.qmd
20250622 - context

Below are estimates of projection accuracy and [calibration plots](#sec-calibrationPlot) for [seasonal](#sec-accuracyProjectionsSeasonal) and [weekly](#sec-accuracyProjectionsWeekly) projections.
Projections were poorly [calibrated](#sec-calibrationIndices) with respect to actual fantasy points.
In general, projected showed a modest tendency to underpredict performance at lower levels of projected points and a moderate-to-strong tendency overpredict performance at higher levels of projected points, an example of the overextremity form of [miscalibration](#sec-calibration).
As a reminder, the overextremity form of [miscalibration](#sec-calibration) is an example of the overprecision form of [overconfidence](#sec-cognitiveBiasesOverconfidence).
That is, projection sources appear to be [overconfident](#sec-cognitiveBiasesOverconfidence) in their projections of player performance.

>>>>

Below are estimates of projection accuracy and [calibration plots](#sec-calibrationPlot) for [seasonal](#sec-accuracyProjectionsSeasonal) and [weekly](#sec-accuracyProjectionsWeekly) projections.
In general, projections showed moderate accuracy in predicting players' fantasy performance.
Projections showed moderate accuracy in terms of [discrimination](#sec-discrimination), based on [$R^2$](#sec-coefficientOfDetermination).
However, projections were not highly accurate.
Projections showed some [miscalibration](#sec-calibrationIndices) with respect to actual fantasy points.
In general, projected showed a modest tendency to underpredict performance at lower levels of projected points and a moderate-to-strong tendency overpredict performance at higher levels of projected points, an example of the overextremity form of [miscalibration](#sec-calibration).
As a reminder, the overextremity form of [miscalibration](#sec-calibration) is an example of the overprecision form of [overconfidence](#sec-cognitiveBiasesOverconfidence).
That is, projection sources appear to be [overconfident](#sec-cognitiveBiasesOverconfidence) in their projections of player performance.
Relatedly, crowd-averaged projections tend to be more accurate than individual sources of projections [CITATION].

### 2025-06-23 simulation.qmd
20250622 - context

>>>>

Below, we perform [bootstrapping](#sec-simulationProjectedPointsBootstrapping) and [Monte Carlo](#sec-simulationProjectedPointsMonteCarlo) simulations of projected statistics and points.
However, it is worth noting that—as for any simulation—the quality of the results depend on the quality of the inputs.
In this case, the quality of the simulation depends on the quality of the projections.
If the projections are no good, the simulation results will not be trustworthy.
Garbage in, garbage out.
As we evaluated in @sec-accuracyProjections, projections tend to show moderate accuracy for fantasy performance, but they are not highly accurate.
Thus, we should treat simulation results arising from fantasy projections with a good dose of skepticism.
